Processing of visual and non-visual naturalistic spatial information in the "parahippocampal place area"

### 2021-01-20 paper/main.tex
write results: consistencies across contrasts

\begin{itemize}
    \item allgemein kürzen; insb. individual results kürzen
    \item consistencies across contrasts ausformulieren
    \item control contrasts ausformulieren
    \item adapt captions of result tables to new phrasing in intro / method
    \item Simons Kommentare, bei denen ich mitunter anderer Meinung bin
    \item ggf. berichten welcher VIS Kontraste jeweils genommen wurde
\end{itemize}

@@

@@

% intro
Lastly, we algorithmically annotated the temporal structure of low-level
perceptual features to create nuisance regressors.
% visual shit
For the AV stimulus, we computed the mean luminance of a movie frame
(\unit[40]{ms}), the difference in mean luminance of each frame's left and right
half, the difference in mean luminance of the lower and upper half, and finally
the perceptual difference of consecutive frames.
% auditory shit
Finally, we computed the left-right difference in volume and root mean square
energy averaged across the length of every movie frame (\unit[40]{ms}) of both
audio-tracks.

@@

% AV: primary contrast
In the primary contrast of the AV stimulus, we contrasted cuts to a setting that
was not depicted before (\texttt{vs\_new}) to cuts that we accompanied with a
change of the camera position within a setting that was already occurring
previously (\texttt{vpe\_old}).
% why
We assumed that movie frames in these categories on average best represent
events that trigger perception of space versus e.g. objects or faces.
% AD: primary contrast
In the primary contrast of the AD stimulus, we contrasted landmarks
\texttt{geo}, and rooms and geometry-defining objects \texttt{geo-room} with all
non-geometry related categories (\texttt{body}, \texttt{bodypart},
\texttt{fahead}, \texttt{object}, \texttt{sex\_f}, \texttt{sex\_m}) except
\texttt{furniture}.
% why se_new & se_old were not used in the primary contrasts
The categories of nouns cueing a setting that occured for the first time
(\texttt{se\_new}) or a setting that recurred during the plot (\texttt{se\_old})
were not included in the primary contrast because
% heterogeneous category
a) categories comprise words that could count as a member of another category
(e.g. ``[a] physician''),
% richness of verbal description vs. picture
b) nouns only vaguely described a scene (e.g. ``[in] Greenbow'', ``[in a]
disco'', ''[black and white] film recordings'') [compared to whole, perceptually
richer pictures], and
% hierarchical categories
c) the narrator is often lacking behind a short dialogue or a change of the
soundscape that might already cued a change of settings.
% furniture
The category ``furniture'' (\texttt{furn}) was not used as a regressor of
interest in any contrast because these nouns could be perceived differently by
different subjects as either a geometry-defining scene element or as an isolated
object.

@@

% intro
Third, we investigated result from both naturalistic paradigms on the level of
individual subjects to ensure that the group results are not just a by-product
of the averaging process.\todo{if you know what I mean}
% AD is the real shit
Focussing on the AD stimulus, we hypothesize[d] that an exclusively auditory
stimulus can/could localize the PPA in individual subjects and thus
possibly substitute a visual paradigm [using blocks of pictures].

@@

% naturalisti stimuli: intro
In the current study, time series of all subjects were analyzed both in subject
space (Z>2.3, p<.05 cluster-corrected) and group space ).
% subject space -> NeuroVault
Results of the analyses that were performed in each subject's [subject-]space
(unthresholded $z$-maps and thresholded $z$-maps, Z>2.3, p<.05 cluster
corrected) can be found in the accompanying datset \todo{Neurvault does not like
unstandardized spaces}
% here report in group space
For better comparions of subjects, we here report results from the analyses
performed in group space (Z>3.4, p<.05 cluster-corrected)
% one contrast to localize them all; "...and Z>3.4 for all"
Contrary to the procedure in \citep{sengupta2016extension}, we used the same
contrast of each naturalistic stimulus and the same threshold [(Z>3.4, p<.05
cluster corrected)] for all subjects.

@@

% report here in group
Results of the primary AD contrast yielded stastically significant bilateral
clusters in nine subjects, and one cluster in the left hemisphere of sub-09,
that are within or overlapping with the individual PPA.
% subj-04
In sub-04, two homologous clusters are apparent, whereas the dedicated localizer
(and AV stimulus) yielded only one cluster in the right hemisphere.
% ref to figure
Figure \ref{fig:subs-thresh-ppa} depicts thresholded $z$-maps of the primary AV
and AD $t$-contrast, and the outline of overlapped, individual PPAs
\citep{sengupta2016extension}.
% MNI space
The $z$-maps and PPA outline are overlayed on the co-registered MNI152 template.
% one slice to show them all
Transversal slice of z=-11 was chosen as it depicts [at least some] voxels of
significant clusters in almost all subjects.

@@

\todo[inline]{anything else to report in the following paragraph? seems more
like just an explanation of the plots}
% Bland-Altman-Plots: why they were done
To better depict/convey the agreement and difference between individual results
of the visual localizer and the primary AD contrast, we created one
Bland-Altman-Plots for each of the 14 subjects (see Figure
\ref{fig:bland-altman}).
% x-axis
The x-axis of every subplot depicts the mean of $z$-values of two spatially
corresponding voxels taken from a subject's unthresholded $z$-map.
% y-axis
The y-axis of every subplot depicts the difference of $z$-values of two
spatially corresponding voxels (dedicated localizer minus AD stimulus).
% masking
Voxels were spatially constrained to a) voxels located in the occipital and
temporal lobes (gray; using the probabilistic Jülich Histological Atlas
\citep{eickhoff2005toolbox, eickhoff2007assignment}), b) voxels located in the
PPA overlap of all subjects (blue), and c) voxels located in individual PPA(s)
(red).
% top KDE plot
A shift of the distribution to voxels with a mean above zero can be seen the
further we constrain voxels to the individual PPA (see KDE plot for the x-axis).
% right KDE plot
Values above the horizontal line depict voxels that show a higher $z$-value in
the dedicated localizer, values below the horizontal line depict voxels that
show higher $z$-value in the AD stimulus.

\begin{figure*}[h!]
\centering
    \includegraphics[scale=0.28]{figures/subjs_bland-altman.png}
    \caption{Bland-Altman-Plots for individual subjects. The x-axis depicts the
        mean of two spatially corresponding voxels in the unthresholded z-map of
        the visual localizer and in the unthresholded z-map of contrast 1 of the
        AD stimulus (KDE plot on the top). The y-axis depicts the difference of
        two voxels (KDE plot on the right).
        The overlays depict voxels spatially contrained to be located in the
        temporal and occipital cortex (gray),
        PPA overlap of all subjects (blue),
        and individual PPA(s) (red).}
    \label{fig:bland-altman}
\end{figure*}

\subsection{Robustness of PPA across contrasts: AV \& AD}

\todo[inline]{tables of significant clusters all contrasts = overkill!? Link to
NeuoVault is added; sign. clusters of all contrasts are listed in the comments}

% AV
In order to test the robustness of our findings, we created four additional
$t$-contrasts for the AV stimulus (see Table \ref{tab:av-contrasts}) to be
investigated on a group level.
%% results: PPA
All of the overall five AV contrasts yielded significant bilateral clusters that
overlap with the PPA group overlap (see Figure \ref{fig:stability-slices}).
[biggest overlap in posterior part of PPA group overlap  = temporal occipital
fusiform cortex] .
% AD
For the AD stimulus, we created overall eight $t$-contrasts (see Table
\ref{tab:ao-contrasts}).
% results
All contrasts except contrast 7 (\texttt{se\_new}, \texttt{se\_old} >
non-spatial categories) and contrast 8 (\texttt{se\_new} > non-spatial
categories) yielded significant bilateral clusters in anterior regions of the
group PPA overlap (see Figure \ref{fig:stability-slices}).
% statement/answer
Results suggest that our findings do not depend on one specific contrasts but
are robust across differently designed contrasts.\todo{concluding statement
often feels like interpretation}
%
\todo[inline]{figure caption: mention / explain other clusters}

% figure group results of robustness across all AD & AV contrasts
\begin{figure*}[h!]
\centering
    \includegraphics[width=\linewidth]{figures/stability-slices}
    \caption{Overlap of significant clusters (Z>3.4; p<.05, cluster corrected)
        The audio-description's contrasts 1-8 (blue; \ref{tab:ao-contrasts})
        are overlaid over the audio-visual movie's contrasts 1-5 (red;
        \ref{tab:av-contrasts}) that were used to [isolate] the PPA
        Cluster are overlaid on top of the MNI152 T1-weighted head template
        (gray).
        Black: outline of overlapping individual PPA ROIs.
        Light gray: The audio-description's field-of-view (cf.
        \citep{hanke2014audiomovie}).}
    \label{fig:stability-slices}
\end{figure*}

\subsection{Non-PPA clusters across contrasts}

% precuneus = retrosplenial cortex ?
\todo[inline]{Following is a list; report depends on the discussion I guess;
anyway: clusters are not ``random'' but make sense which speaks for the use of
naturalistic stimuli}

\subsubsection{AV}

\begin{itemize}
    \item RSC: 3 contrasts (all bilat; vse\_new > vpe\_old; vse\_new >
        vse\_old, vpe\_old; vse\_new, vpe\_new > vpe\_old)
    \item lateral occipital cortex: 4 contrasts (all except vse\_new > vse\_old; all bilateral)
\end{itemize}

\subsubsection{AD}

\begin{itemize}
\item RSC (and ventral precuneus): 7 contrasts (all bilateral)
\item lateral occipital cortex: 6 contrasts (4 bilateral, 2 unilateral =
    transverse occipital sulcus / occipiatal place area?; AD \& AV clusters
    overlap but AD clusters are more lateral, AV cluster are more medial \&
    caudal)
\item right superior temporal gyrus (auditory cortices): 4 contrasts
\item (smallish) prefrontal clusters: 3 contrasts (non-overlapping)
\end{itemize}

\subsection{control contrasts (AV \& AD)}

\todo[inline]{contrasts are mentioned in the method section; shall results be
reported (and later discussed)?}

>>>>

\begin{itemize}
    \item kürzen (war nicht ganz einfach)
    \item control contrasts ausformulieren
    \item adapt captions of result tables to new phrasing in intro / method
    \item Simons Kommentare, bei denen ich mitunter anderer Meinung bin
    \item ggf. berichten welcher VIS Kontraste jeweils genommen wurde
\end{itemize}

@@

% low-leve confounds: intro
Lastly, we algorithmically annotated the temporal structure of low-level
perceptual features to create nuisance regressors.
% visual shit
For the AV stimulus, we computed the mean luminance of a movie frame
(\unit[40]{ms}), the difference in mean luminance of each frame's left and right
half, the difference in mean luminance of the lower and upper half, and finally
the perceptual difference of consecutive frames.
% auditory shit
Finally, we computed the left-right difference in volume and root mean square
energy averaged across the length of every movie frame (\unit[40]{ms}) of both
audio-tracks.

@@

@@

% AV: primary contrast
In the primary contrast of the AV stimulus, we contrasted cuts to a setting that
was not depicted before (\texttt{vs\_new}) to cuts that we accompanied with a
change of the camera position within a setting that was already occurring
previously (\texttt{vpe\_old}).
% why
We assumed that movie frames in these categories on average best represent
events that trigger perception of space versus e.g. objects or faces.
% AD: primary contrast
In the primary contrast of the AD stimulus, we contrasted landmarks
\texttt{geo}, and rooms and geometry-defining objects \texttt{geo-room} with all
non-geometry related categories (\texttt{body}, \texttt{bodypart},
\texttt{fahead}, \texttt{object}, \texttt{sex\_f}, \texttt{sex\_m}) except
\texttt{furniture}.
% why se_new & se_old were not used in the primary contrasts
The categories of nouns cueing a setting that occurred for the first time
(\texttt{se\_new}) or a setting that recurred during the plot (\texttt{se\_old})
were not included in the primary contrast because
% heterogeneous category
a) categories comprise words that could count as a member of another category
(e.g. ``[a] physician''),
% richness of verbal description vs. picture
b) nouns only vaguely described a scene (e.g. ``[in] Greenbow'', ``[in a]
disco'', ''[black and white] film recordings'') [compared to whole, perceptually
richer pictures], and
% hierarchical categories
c) the narrator is often lacking behind a short dialogue or a change of the
soundscape that might already cued a change of settings.
% furniture
The category ``furniture'' (\texttt{furn}) was not used as a regressor of
interest in any contrast because these nouns could be perceived differently by
different subjects as either a geometry-defining scene element or as an isolated
object.

@@

% intro
Third, we investigated result from both naturalistic paradigms on the level of
individual subjects to ensure that the group results are not just a by-product
of the averaging process.
% AD is the real shit
Focussing on the AD stimulus, we hypothesize[d] that an exclusively auditory
stimulus can/could localize the PPA in individual subjects and thus
possibly substitute a visual paradigm [using blocks of pictures].

@@

% naturalisti stimuli: intro
In the current study, time series of all subjects were analyzed both in subject
space (Z>2.3, p<.05 cluster-corrected) and group space ).
% subject space -> NeuroVault
Results of the analyses that were performed in each subject's [subject-]space
(unthresholded $z$-maps and thresholded $z$-maps, Z>2.3, p<.05 cluster
corrected) can be found in the accompanying dataset. \todo{Neurovault does not
like unstandardized spaces}
% here report in group space
For better comparisons of subjects, we here report results from the analyses
performed in group space (Z>3.4, p<.05 cluster-corrected)
% one contrast to localize them all; "...and Z>3.4 for all"
Contrary to the procedure in \citep{sengupta2016extension}, we used the same
contrast of each naturalistic stimulus and the same threshold [(Z>3.4, p<.05
cluster corrected)] for all subjects.

@@

% report here in group
Results of the primary AD contrast yielded statically significant bilateral
clusters in nine subjects, and one cluster in the left hemisphere of sub-09,
that are within or overlapping with the individual PPA.
% subj-04
In sub-04, two homologous clusters are apparent, whereas the dedicated localizer
(and AV stimulus) yielded only one cluster in the right hemisphere.
% ref to figure
Figure \ref{fig:subs-thresh-ppa} depicts thresholded $z$-maps of the primary AV
and AD $t$-contrast, and the outline of overlapped, individual PPAs
\citep{sengupta2016extension}.
% MNI space
The $z$-maps and PPA outline are overlayed on the co-registered MNI152 template.
% one slice to show them all
Transversal slice of z=-11 was chosen as it depicts [at least some] voxels of
significant clusters in almost all subjects.

@@

% Bland-Altman-Plots: why they were done
To better depict/convey the agreement and difference between individual results
of the visual localizer and the primary AD contrast, we created one
Bland-Altman-Plots for each of the 14 subjects (see Figure
\ref{fig:bland-altman}).
% top KDE plot
A shift of the distribution to voxels with a mean above zero can be seen the
further we constrain voxels to the individual PPA (see KDE plot for the x-axis).
% right KDE plot
Values above the horizontal line depict voxels that show a higher $z$-value in
the dedicated localizer, values below the horizontal line depict voxels that
show higher $z$-value in the AD stimulus.

\begin{figure*}[h!]
\centering
    \includegraphics[scale=0.27]{figures/subjs_bland-altman.png}
    \caption{Bland-Altman-Plots for individual subjects.
    The x-axes show the means of two spatially corresponding voxels in the
    unthresholded $z$-map of the audio-description's primary contrast and
    unthresholded $z$-map of the visual localizer (KDE plot on the top).
    The y-axes show the difference of two voxels (localizer minus
    audio-description; KDE plot on the right).
    The overlays depict voxels spatially constrained to the
    temporal and occipital cortex (gray; based on the probabilistic Jülich
    Histological Atlas \citep{eickhoff2005toolbox, eickhoff2007assignment}),
    PPA overlap of all subjects (blue),
    and individual PPA(s) (red).}
    \label{fig:bland-altman}
\end{figure*}

\subsection{Robustness of group results across contrasts}

% unthresholded $z$-maps of all contrasts on a group level:
% \href{https://neurovault.org/collections/KADGMGVZ/}{NeuroVault}.

% AV
In order to test the robustness of our findings, we created four additional
$t$-contrasts for the AV stimulus (see Table \ref{tab:av-contrasts}) to be
investigated on a group level.
% results: PPA; biggest overlap in posterior part of PPA group overlap  =
%temporal occipital fusiform cortex
All of the overall five AV contrasts yielded significant bilateral clusters that
overlap with the PPA group overlap (see Figure \ref{fig:stability-slices}).
% AD
For the AD stimulus, we created overall eight $t$-contrasts (see Table
\ref{tab:ao-contrasts}).
% results
All contrasts except contrast 7 (\texttt{se\_new}, \texttt{se\_old} >
non-spatial categories) and contrast 8 (\texttt{se\_new} > non-spatial
categories) yielded significant bilateral clusters in anterior regions of the
group PPA overlap (see Figure \ref{fig:stability-slices}).
% statement/answer
Results suggest that our findings do not depend on one specific contrasts but
are robust across differently designed contrasts.\todo{concluding statement
often feels like interpretation}

% AV
Reliably across the five contrasts of the AV stimulus, we also find bilaterally
significant clusters also in the precuneal cortex (contrasts 1, 3, 4; all
bilateral)\todo{and? -> fsleyes} and lateral occipital cortex (all contrasts
except contrast 3)
% AD; LOC: AV cluster are more medial, AD clusters are more lateral
Reliably across the five contrasts of the AD, we find bilaterally significant
clusters in the ventral precuneus (7 contrasts), lateral occipital cortex
(bilateral in 4 contrasts, unilateral in 2 contrasts), superior temporal
cortices (4 contrasts)\todo{uni/bilateral?}.
%
\todo[inline]{(smallish) prefrontal clusters: 3 contrasts (non-overlapping)}

\begin{figure*}[h!]
\centering
    \includegraphics[width=\linewidth]{figures/stability-slices}
    \caption{Overlap of significant clusters (Z>3.4; p<.05, cluster corrected)
        The audio-description's contrasts 1-8 (blue; \ref{tab:ao-contrasts})
        are overlaid over the audio-visual movie's contrasts 1-5 (red;
        \ref{tab:av-contrasts}).
        Cluster are overlaid on top of the MNI152 T1-weighted head template
        (gray).
        Black: outline of overlapping individual PPA ROIs.
        Light gray: The audio-description's field-of-view (cf.
        \citep{hanke2014audiomovie}).
        The figure shows that some contrasts yielded significant clusters
        also in the lateral temporal and prefrontal cortex.
        }
    \label{fig:stability-slices}
\end{figure*}

\subsection{control contrasts}
